Incorporating periodic variability in hidden Markov models for animal movement

### 2016-02-29 paper3.Rnw
maybe save everything to RDS?

<<BICred_plot cat131,warning=FALSE,echo=FALSE,message=FALSE,fig.cap="Change in BIC across models, cat \\#131.  $\\dbic$ is scaled individually per model, so that $\\dbic=0$ represents the BIC-optimal number of states for a particular model.",fig.width=6,fig.height=4>>=
load("cat2allmod.RData")
df2 <- transform(allmodsumdf,
            distrib=ifelse(grepl("LN",model),"log-Normal","Weibull"),
            turn_angle=ifelse(grepl("VM",model),"yes","no"),
            homog=ifelse(grepl("HMM",model),"homogeneous HMM","time-heterogeneous HMM"))
ggplot(df2, aes(x=nstates,y=deltaBIC,colour=distrib,lty=turn_angle))+
    geom_line()+
    facet_wrap(~ homog)+
    scale_colour_brewer(name="step length\ndistribution",palette="Set1")+
    ## scale_size_continuous( name="# parameters") +
    #    geom_point(aes(size=parameters))+
    scale_linetype(name="von Mises\nturning angle?")+
    labs(y=expression(Delta*"BIC"),
         x="Number of States")+
    geom_hline(yintercept=0,colour="gray")+
    zmargin
@

>>>>

<<BICred_plot cat131,warning=FALSE,echo=FALSE,message=FALSE,fig.cap="Change in BIC across models, cat \\#131.  $\\dbic$ is scaled individually per model, so that $\\dbic=0$ represents the BIC-optimal number of states for a particular model.",fig.width=6,fig.height=4>>=
allmodsumdf <- readRDS("cat2allmod.RDS")
df2 <- transform(allmodsumdf,
            distrib=ifelse(grepl("LN",model),"log-Normal","Weibull"),
            turn_angle=ifelse(grepl("VM",model),"yes","no"),
            homog=ifelse(grepl("HMM",model),"homogeneous HMM","time-heterogeneous HMM"))
ggplot(df2, aes(x=nstates,y=deltaBIC,colour=distrib,lty=turn_angle))+
    geom_line()+
    facet_wrap(~ homog)+
    scale_colour_brewer(name="step length\ndistribution",palette="Set1")+
    ## scale_size_continuous( name="# parameters") +
    #    geom_point(aes(size=parameters))+
    scale_linetype(name="von Mises\nturning angle?")+
    labs(y=expression(Delta*"BIC"),
         x="Number of States")+
    geom_hline(yintercept=0,colour="gray")+
    zmargin
@
